---
title: "Split-Data"
author: "James Bressani"
date: "April 13, 2025"
output: html_document
---
## Split Data Documentation

## splitData()

Splits a dataset into a training and testing set based off of a ratio given.

### Arguments:

- `df`: Dataset to split (dataframe)
- `trainingRatio`: Proportion for training (default is 80%)
- `seed`: For reproducible results (default is null)

### Returns:

List containing `train` and `test` datasets

```{r}
#How to use SplitData() function
cars <- mtcars
head(cars)

cars <- splitData(cars, )

#Use variables to extract the new dataframes
trainingOne <- cars$training
testingOne <- cars$testing

#
str(trainingOne)
str(testingOne)
```

## compareData()

Compares performance of two pre-trained models on the same test data.

### Arguments:

`test_data`: Test dataset for evaluation (data frame)
`model1`: Model 1
`model2`: Model 2
`target`: Name of target variable
`metrics`: Performance metrics to calculate

### Returns:

Data frame with performance metrics for both models

```{r}
# model1 <- lm(mpg ~ wt + hp, data = trainData)
# model2 <- lm(mpg ~ wt + hp + cyl, data = trainData)
# 
# results <- compareData(testData, model1, model2, target = "mpg")
# results
```

## compareGraph()

### Arguments:

`comparison_results`: Results from compareData() (data frame)
`plot_type`: Type of visualization (string: "metrics", "residuals", or "actual_vs_predicted")

### Returns:

ggplot2 visualization comparing the models

```{r}
# graph1 <- compareGraph(results, plot_type = "metrics")
# plot(graph1)

```
