---
title: "SplitData"
author: "James Bressani"
date: "April 30, 2025"
output: html_document
---
## Split Data Documentation

## splitData()

Splits a dataset into a training and testing set based off of a ratio given.

### Arguments:

- `df`: Dataset to split (dataframe)
- `trainingRatio`: Proportion for training (default is 80%)
- `seed`: For reproducible results (default is null)

### Returns:

List containing `train` and `test` datasets

```{r}
#How to use SplitData() function
flowers <- iris
head(flowers)

flowers <- splitData(flowers, trainingRatio = 0.8, seed = NULL)

#Use variables to extract the new dataframes
trainingOne <- flowers$training
testingOne <- flowers$testing

#checking structure of the new data
str(trainingOne)
str(testingOne)
```

## compareData()

Compares performance of two pre-trained models on the same test data.

### Arguments:

`df`: Test dataset for evaluation (dataframe)
`model1`: Model 1
`model2`: Model 2
`x`: Name of the target variable
`metrics`: Performance metrics to calculate

### Returns:

Dataframe with performance metrics for both models

```{r}
model1 <- lm(Sepal.Length ~ Petal.Length + Petal.Width, data = trainingOne)
model2 <- lm(Sepal.Length ~ Petal.Length + Petal.Width + Species, data = trainingOne)

results <- compareData(testingOne, model1, model2, x = "Sepal.Length")
results
```

## compareGraph()

### Arguments:

`compareDataResults`: Results from compareData() (dataframe)
`plot`: Type of visualization (metrics, residuals, or actualvspredicted)

### Returns:

ggplot2 visualization comparing the models

```{r}
comparison <- compareGraph(results, plot = "metrics")
comparison

```
